Mathematical description of Naomi

### 2022-12-09 src/example_naomi/maths.Rmd
Fixes to maths

**Flag for not understanding** ART coverage at $T_3$ is modelled by 
$$
\text{logit}(\alpha_{x, s, a, {T_2}}) = \text{logit}(\alpha_{x, s, a, {T_1}}) + \eta_{R_x, s, a, {T_3}}^\alpha
$$

@@

* Number of PLHIV on ART is $A_{x, s, a, t} = N_{x, s, a, t} \cdot \rho_{x, s, a, t} \cdot \alpha_{x, s, a, t}$
* Let $\gamma_{x, x', t} \in [0, 1]$ be the probability that a person of ART residing in district $x$ recieves ART in district $x'$ at time $t$
* We assume that $\gamma_{x, x', t} = 0$ for $x \notin \{x, \text{ne}(x)\}$ i.e. that individuals seek treatment only in their residing district and its neighbours $\text{ne}(x) = \{x': x' \sim x\}$ where $\sim$ is an adjacency relation
  * $\sum_{x' \in \{x, \text{ne}(x)\}} \gamma_{x, x', t} = 1$
* Model $\gamma_{x, x', t}$ with a multinomial logit model where $\tilde \gamma_{x, t}$ is the log odds ratio of seeking ART in the district $x'$ neighbouring $x$ **flag for confusion here**
\begin{align}
\tilde \gamma_{x, t} &= \tilde \gamma_0 + u_x^{\tilde \gamma} + u_x^{\tilde \gamma, t = T_2} \\ 
\tilde \gamma_0 &= -4 \\
u_x^{\tilde \gamma} &\sim \mathcal{N}(0, \sigma_X^{\tilde \gamma}) \\
u_x^{\tilde \gamma, t \in \{T_2, T_3\}} &\sim \mathcal{N}(0, \sigma_{XT}^{\tilde \gamma}) 
\end{align}
  * $\tilde \gamma_{x, t}$ is an intercept specifying the prior mean for the log odds of seeking ART in each neighbouring district compared to the home district
  * $u_x^{\tilde \gamma}$ are district random effects
  * $u_x^{\tilde \gamma, t \in \{T_2, T_3\}}$ is the change in district level log-odds ratios between $T_1$ and $T_2$ -- **flag for confusion: shouldn't this just be $t = T_2$ here**
  * Note: only one value estimated for each district, implying no preference between neighbouring districts, and no sex-age specific modelling
* Calculate multinomial probabilities via softmax (n.b. this is the sigmoid function, the inverse of the softmax)
$$
\gamma_{x, x', t} = \frac{1}{1 + \sum_{x^\star \sim x} \exp(\tilde \gamma_{x^\star, t})}
$$
* The number of ART clients who reside in district $x$ and obtain ART in district $x'$ are $A_{x, x', s, a, t} = A_{x, s, a, t} \cdot \gamma_{x, x', t} = N_{x, s, a, t} \cdot \rho_{x, s, a, t} \cdot \alpha_{x, s, a, t} \cdot \gamma_{x, x', t}$
* Total attending ART facilities in district $x'$ is $\tilde A_{x', s, a, t} = \sum_{x \sim x', x = x'} A_{x, x', s, a, t}$

@@

* Let $\nu$ be a household survey occuring at $T_1$
* Furnishes weighted observations for HIV prevalence $\hat \rho_{\{x\}, \{s\}, \{a\}, \nu}$, ART coverage $\hat \alpha_{\{x\}, \{s\}, \{a\}, \nu}$ and proportion recently infected $\hat \kappa_{\{x\}, \{s\}, \{a\}, \nu}$ with respective Kish effective sample sizes $M^{\hat \theta}_{\{x\}, \{s\}, \{a\}, \nu}$ for $\theta \in \{\rho, \alpha, \kappa\}$
* The observed cases are $Y^{\hat \theta}_{\{x\}, \{s\}, \{a\}, \nu} = M^{\hat \theta}_{\{x\}, \{s\}, \{a\}, \nu} \cdot \hat \theta_{\{x\}, \{s\}, \{a\}, \nu}$
* For HIV prevalence we use a binomial working likelihood
\begin{align}
Y^{\hat \rho}_{\{x\}, \{s\}, \{a\}, \nu} &\sim \text{Bin}(M^{\hat \rho}_{\{x\}, \{s\}, \{a\}, \nu}, \rho_{\{x\}, \{s\}, \{a\}, {T_1}}) \\
\rho_{\{x\}, \{s\}, \{a\}, t} &= \frac{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t} \cdot \rho_{x, s, a, t}}{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t}}
\end{align}
* For ART coverage we also use a binomial working likelihood
\begin{align}
Y^{\hat \alpha}_{\{x\}, \{s\}, \{a\}, \nu} &\sim \text{Bin}(M^{\hat \alpha}_{\{x\}, \{s\}, \{a\}, \nu}, \alpha_{\{x\}, \{s\}, \{a\}, {T_1}}) \\
\alpha_{\{x\}, \{s\}, \{a\}, t} &= \frac{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t} \cdot \rho_{x, s, a, t} \cdot \alpha_{x, s, a, t}}{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t} \cdot \rho_{x, s, a, t}}
\end{align}
* For recent infections we also use a binomial working likelihood
\begin{align}
Y^{\hat \kappa}_{\{x\}, \{s\}, \{a\}, \nu} &\sim \text{Bin}(M^{\hat \kappa}_{\{x\}, \{s\}, \{a\}, \nu}, \kappa_{\{x\}, \{s\}, \{a\}, {T_1}}) \\
\kappa_{x, s, a, t} &= 1 - \exp(- \lambda_{x, s, a, t} \cdot \frac{1 - \rho_{x, s, a, t}}{\rho_{x, s, a, t}} \cdot (\Omega_T - \beta_T ) - \beta_T ) \\
\Omega_T &\sim \mathcal{N}(\Omega_{T_0}, \sigma^{\Omega_T}) \\
\beta_T &\sim \mathcal{N}(\beta_{T_0}, \sigma^{\beta_T})
\end{align}
  * $\kappa_{x, s, a, t}$ are the predicted proportion recently infected among HIV positive persons
  * $\Omega_T$ is the mean duration of recent infection (MDRI)
    * Use an informative prior based on the characteristics of the recent infection testing algorithm (RITA)
    * For PHIA surveys $\Omega_{T_0} = 130 \text{ days}$ and $\sigma^{\Omega_T} = 6.12 \text{ days}$
    * **Flag: what about for other surveys?*
  * $\beta_T$ is the false recent ratio (FRR)
    * For PHIA surveys $\beta_{T_0} = 0.0$ and $\sigma^{\beta_T} = 0.0$. **Flag: is this just assuming that there is no false recency? How is this assumption justified?*

@@

* Include two years of ANC testing data: the year of the most recent survey $Y[T_1]$ and the current year $Y[T_2]$
* $W^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients
* $X^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients with ascertained status
* $Y^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients with positive status (either known or tested)
* $Z^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients already on ART prior to first ANC
* Sometimes ANC testing data are only available for part of a given year, for example only the first three quarters. Denote $M^\text{ANC}_{Y[t]} \in \{1, \ldots, 12\}$ the number of months of reported data reflected in counts for year $Y[t]$
* Likelihood for number of ANC clients specified only for year $Y[T_2]$ (**why?**) as
$$
W_{\{x\} Y[T_2]}^{\text{ANC}} \sim \text{Pois} \left( \frac{M_{Y[T 2]}^{\text{ANC}}}{12} \sum_{x \in\{x\}} \sum_{a \in\{15, \ldots 45\}} \Psi_{x, a, T_2} \right)
$$
* Observed number of HIV positive and already on ART among ANC clients at both $Y[T_1]$ and $Y[T_2]$ are modelled by
\begin{aligned}
& Y_{\{x\} Y[t]}^{\text{ANC}} &\sim \text{Bin} \left(X_{\{x\} Y[t]}^{\text{ANC}}, \rho_{\{x\},\{15, \ldots 49\}, t}^{\text{ANC}}\right) \\
& Z_{\{x\} Y[t]}^{\text{ANC}} &\sim \text{Bin} \left(Y_{\{x\} Y[t]}^{\text{ANC}}, \alpha_{\{x\},\{15, \ldots 49\}, t}^{\text{ANC}}\right)
\end{aligned}
where predicted prevalence and ART coverage are aggregated weighted by the predicted number of pregnant women by age $\Psi_{x, a, t}$
\begin{aligned}
\rho_{\{x\}\{a\}, t}^{\text{ANC}} &= \frac{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t} \cdot \rho_{x, a, t}^{\text{ANC}}}{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t}} \\
\alpha_{\{x\}\{a\}, t}^{\text{ANC}} &= \frac{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t} \cdot \rho_{x, a, t}^{\text{ANC}} \cdot \alpha_{x, a, t}^{\text{ANC}}}{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t} \cdot \rho_{x, a, t}^{\text{ANC}}}
\end{aligned}

@@

* Let $\dot A_{\{x\}, \{s\}, \{a\}, t}$ be data for the number receiving ART **flag: confusion about the notation here. In general would be good to define precisely what is meant by $\{x\}$. Presumably the LHS below is a set, yet the RHS is a sum over the sets so I think just a number -- so how can the two be equal?**
$$
\dot A_{\{x\}, \{s\}, \{a\}, t} = \sum_{s \in \{s\}} \sum_{a \in \{a\}} \sum_{x \in \{x\}} \sum_{x \sim x', x = x'} \dot A_{x', x, s, a, t}
$$
* Model the unobserved numbers of ART clients travelling from $x'$ to $x$ as
$$
\dot A_{x', x, s, a, t} \sim \text{Bin}(N_{x', s, a, t}, \pi_{x', x, s, a, t})
$$
where $\pi_{x', x, s, a, t} = \rho_{x', s, a, t} \cdot \alpha_{x', s, a, t} \cdot \gamma_{x', s, a, t}$ **flag: should this be $\gamma_{x', x, s, a, t}$ since it's people moving from $x'$ to $x$ (and so far no where in the RHS is there an $x$ which is suspicious)**
* This likelihood is approximated using a normal for the sum of binomials
$$
\dot A_{\{x\}, \{s\}, \{a\}, t} \sim \mathcal{N}(\tilde) A_{\{x\}, \{s\}, \{a\}, t}, \sigma^{\tilde A}_{\{x\}, \{s\}, \{a\}, t})
$$
where
  * $\tilde{A}_{\{x\},\{s\}\{a\}, t} = \sum_{s \in\{s\}} \sum_{a \in\{a\}} \sum_{x \in\{x\}} \sum_{x \sim x', x = x'} N_{x', s, a, t} \cdot \pi_{x', x, s, a, t}$
  * $\sigma_{\{x\},\{s\}\{a\}, t}^{\tilde{A}} = \sqrt{\sum_{s \in\{s\}} \sum_{a \in\{a\}} \sum_{x \in\{x\}} \sum_{x \sim x^', x=x \prime} N_{x^', s, a, t} \cdot \pi_{x^', x, s, a, t} \cdot \left(1-\pi_{x^', x, s, a, t}\right)}$

@@

* Not sure what $R_x$ means. Is it like $R_x: \mathcal{X} \to \mathcal{X}$
* Some confusion on how to offset terms work -- they seem cool though. Might prefer they not be called $\eta$ which is in my head linear predictor
  * $\eta^\lambda_{R_x, s, a, t}$ aren't these $R_x, s, a, t$ specific rather than 
* Aggregation over age 15-49 uses sum from $a = 15$ to $a = 45$? Perhaps this is because $a = 45$ actually corresponds to the age band 45-49. Edit: yes, $a = 45$ corresponds to 45-49
* Sometimes in subscript we have $x, s, a, t$ and sometimes e.g. $x, s, at$ -- why?
* Why $\sigma^\lambda \sim \mathcal{N}^+(0, 1)$ rather than e.g. $\sigma^\lambda \sim \mathcal{N}^+(0, 2.5)$
* Inconsistent use of $T2$ and $T_2$ in the appendix (I prefer the subscript so try to use throughout here)
* In softmax function, confused as to what this equation is saying: shouldn't there be an equals sign in there before the large brackets?
* What's $Y[T2][T1]$ is this a typo and should be $Y[T1]$ -- in "The observed number of HIV positive and already on ART..."
* "In cases where some data inputs, some model..." should be "In cases where some data inputs **are missing**, some model..."

>>>>

ART coverage at $T_3$ is modelled by^[Don't understand this.]
$$
\text{logit}(\alpha_{x, s, a, {T_2}}) = \text{logit}(\alpha_{x, s, a, {T_1}}) + \eta_{R_x, s, a, {T_3}}^\alpha
$$

@@

* Number of PLHIV on ART is $A_{x, s, a, t} = N_{x, s, a, t} \cdot \rho_{x, s, a, t} \cdot \alpha_{x, s, a, t}$
* Let $\gamma_{x, x', t} \in [0, 1]$ be the probability that a person of ART residing in district $x$ recieves ART in district $x'$ at time $t$
* We assume that $\gamma_{x, x', t} = 0$ for $x \notin \{x, \text{ne}(x)\}$ i.e. that individuals seek treatment only in their residing district and its neighbours $\text{ne}(x) = \{x': x' \sim x\}$ where $\sim$ is an adjacency relation
  * $\sum_{x' \in \{x, \text{ne}(x)\}} \gamma_{x, x', t} = 1$
* Model $\gamma_{x, x', t}$ with a multinomial logit model where $\tilde \gamma_{x, t}$ is^[Confused by this notation.] the log odds ratio of seeking ART in the district $x'$ neighbouring $x$
\begin{align}
\tilde \gamma_{x, t} &= \tilde \gamma_0 + u_x^{\tilde \gamma} + u_x^{\tilde \gamma, t = T_2} \\ 
\tilde \gamma_0 &= -4 \\
u_x^{\tilde \gamma} &\sim \mathcal{N}(0, \sigma_X^{\tilde \gamma}) \\
u_x^{\tilde \gamma, t \in \{T_2, T_3\}} &\sim \mathcal{N}(0, \sigma_{XT}^{\tilde \gamma}) 
\end{align}
  * $\tilde \gamma_{x, t}$ is an intercept specifying the prior mean for the log odds of seeking ART in each neighbouring district compared to the home district
  * $u_x^{\tilde \gamma}$ are district random effects
  * $u_x^{\tilde \gamma, t \in \{T_2, T_3\}}$ is^[Shouldn't this just be $t = T_2$ here rather than $t \in \{T_2, T_3\}$?] the change in district level log-odds ratios between $T_1$ and $T_2$
  * Note: only one value estimated for each district, implying no preference between neighbouring districts, and no sex-age specific modelling
* Calculate multinomial probabilities via softmax (n.b. this is the sigmoid function, the inverse of the softmax)
$$
\gamma_{x, x', t} = \frac{1}{1 + \sum_{x^\star \sim x} \exp(\tilde \gamma_{x^\star, t})}
$$
* The number of ART clients who reside in district $x$ and obtain ART in district $x'$ are $A_{x, x', s, a, t} = A_{x, s, a, t} \cdot \gamma_{x, x', t} = N_{x, s, a, t} \cdot \rho_{x, s, a, t} \cdot \alpha_{x, s, a, t} \cdot \gamma_{x, x', t}$
* Total attending ART facilities in district $x'$ is $\tilde A_{x', s, a, t} = \sum_{x \sim x', x = x'} A_{x, x', s, a, t}$

@@

* Let $\nu$ be a household survey occuring at $T_1$
* Furnishes weighted observations for HIV prevalence $\hat \rho_{\{x\}, \{s\}, \{a\}, \nu}$, ART coverage $\hat \alpha_{\{x\}, \{s\}, \{a\}, \nu}$ and proportion recently infected $\hat \kappa_{\{x\}, \{s\}, \{a\}, \nu}$ with respective Kish effective sample sizes $M^{\hat \theta}_{\{x\}, \{s\}, \{a\}, \nu}$ for $\theta \in \{\rho, \alpha, \kappa\}$
* The observed cases are $Y^{\hat \theta}_{\{x\}, \{s\}, \{a\}, \nu} = M^{\hat \theta}_{\{x\}, \{s\}, \{a\}, \nu} \cdot \hat \theta_{\{x\}, \{s\}, \{a\}, \nu}$
* For HIV prevalence we use a binomial working likelihood
\begin{align}
Y^{\hat \rho}_{\{x\}, \{s\}, \{a\}, \nu} &\sim \text{Bin}(M^{\hat \rho}_{\{x\}, \{s\}, \{a\}, \nu}, \rho_{\{x\}, \{s\}, \{a\}, {T_1}}) \\
\rho_{\{x\}, \{s\}, \{a\}, t} &= \frac{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t} \cdot \rho_{x, s, a, t}}{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t}}
\end{align}
* For ART coverage we also use a binomial working likelihood
\begin{align}
Y^{\hat \alpha}_{\{x\}, \{s\}, \{a\}, \nu} &\sim \text{Bin}(M^{\hat \alpha}_{\{x\}, \{s\}, \{a\}, \nu}, \alpha_{\{x\}, \{s\}, \{a\}, {T_1}}) \\
\alpha_{\{x\}, \{s\}, \{a\}, t} &= \frac{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t} \cdot \rho_{x, s, a, t} \cdot \alpha_{x, s, a, t}}{\sum_{x \in \{x\}} \sum_{s \in \{s\}} \sum_{a \in \{a\}} N_{x, s, a, t} \cdot \rho_{x, s, a, t}}
\end{align}
* For recent infections we also use a binomial working likelihood
\begin{align}
Y^{\hat \kappa}_{\{x\}, \{s\}, \{a\}, \nu} &\sim \text{Bin}(M^{\hat \kappa}_{\{x\}, \{s\}, \{a\}, \nu}, \kappa_{\{x\}, \{s\}, \{a\}, {T_1}}) \\
\kappa_{x, s, a, t} &= 1 - \exp(- \lambda_{x, s, a, t} \cdot \frac{1 - \rho_{x, s, a, t}}{\rho_{x, s, a, t}} \cdot (\Omega_T - \beta_T ) - \beta_T ) \\
\Omega_T &\sim \mathcal{N}(\Omega_{T_0}, \sigma^{\Omega_T}) \\
\beta_T &\sim \mathcal{N}(\beta_{T_0}, \sigma^{\beta_T})
\end{align}
  * $\kappa_{x, s, a, t}$ are the predicted proportion recently infected among HIV positive persons
  * $\Omega_T$ is the mean duration of recent infection (MDRI)
    * Use an informative prior based on the characteristics of the recent infection testing algorithm (RITA)
    * For PHIA surveys^[What about other surveys?] $\Omega_{T_0} = 130 \text{ days}$ and $\sigma^{\Omega_T} = 6.12 \text{ days}$
  * $\beta_T$ is the false recent ratio (FRR)
    * For PHIA surveys $\beta_{T_0} = 0.0$ and $\sigma^{\beta_T} = 0.0$.^[Is this just assuming that there is no false recency? How is this assumption justified?]

@@

* Include two years of ANC testing data: the year of the most recent survey $Y[T_1]$ and the current year $Y[T_2]$
* $W^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients
* $X^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients with ascertained status
* $Y^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients with positive status (either known or tested)
* $Z^\text{ANC}_{\{x\}, Y[t]}$ are the number of ANC clients already on ART prior to first ANC
* Sometimes ANC testing data are only available for part of a given year, for example only the first three quarters. Denote $M^\text{ANC}_{Y[t]} \in \{1, \ldots, 12\}$ the number of months of reported data reflected in counts for year $Y[t]$
* Likelihood for number of ANC clients specified only^[Why?] for year $Y[T_2]$ as
$$
W_{\{x\} Y[T_2]}^{\text{ANC}} \sim \text{Pois} \left( \frac{M_{Y[T 2]}^{\text{ANC}}}{12} \sum_{x \in\{x\}} \sum_{a \in\{15, \ldots 45\}} \Psi_{x, a, T_2} \right)
$$
* Observed number of HIV positive and already on ART among ANC clients at both $Y[T_1]$ and $Y[T_2]$ are modelled by
\begin{aligned}
& Y_{\{x\} Y[t]}^{\text{ANC}} &\sim \text{Bin} \left(X_{\{x\} Y[t]}^{\text{ANC}}, \rho_{\{x\},\{15, \ldots 49\}, t}^{\text{ANC}}\right) \\
& Z_{\{x\} Y[t]}^{\text{ANC}} &\sim \text{Bin} \left(Y_{\{x\} Y[t]}^{\text{ANC}}, \alpha_{\{x\},\{15, \ldots 49\}, t}^{\text{ANC}}\right)
\end{aligned}
where predicted prevalence and ART coverage are aggregated weighted by the predicted number of pregnant women by age $\Psi_{x, a, t}$
\begin{aligned}
\rho_{\{x\}\{a\}, t}^{\text{ANC}} &= \frac{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t} \cdot \rho_{x, a, t}^{\text{ANC}}}{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t}} \\
\alpha_{\{x\}\{a\}, t}^{\text{ANC}} &= \frac{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t} \cdot \rho_{x, a, t}^{\text{ANC}} \cdot \alpha_{x, a, t}^{\text{ANC}}}{\sum_{x \in\{x\}} \sum_{a \in\{a\}} \Psi_{x, a, t} \cdot \rho_{x, a, t}^{\text{ANC}}}
\end{aligned}

@@

* Let $\dot A_{\{x\}, \{s\}, \{a\}, t}$ be data for the number receiving ART^[I'm confused about the notation here. In general would be good to define precisely what is meant by $\{x\}$. Presumably the LHS below is a set, yet the RHS is a sum over the sets so I think just a number -- so how can the two be equal?]
$$
\dot A_{\{x\}, \{s\}, \{a\}, t} = \sum_{s \in \{s\}} \sum_{a \in \{a\}} \sum_{x \in \{x\}} \sum_{x \sim x', x = x'} \dot A_{x', x, s, a, t}
$$
* Model the unobserved numbers of ART clients travelling from $x'$ to $x$ as
$$
\dot A_{x', x, s, a, t} \sim \text{Bin}(N_{x', s, a, t}, \pi_{x', x, s, a, t})
$$
where $\pi_{x', x, s, a, t} = \rho_{x', s, a, t} \cdot \alpha_{x', s, a, t} \cdot \gamma_{x', s, a, t}$^[Should this be $\gamma_{x', x, s, a, t}$ since it's people moving from $x'$ to $x$ (and so far no where in the RHS is there an $x$ which is suspicious)]
* This likelihood is approximated using a normal for the sum of binomials
$$
\dot A_{\{x\}, \{s\}, \{a\}, t} \sim \mathcal{N}(\tilde) A_{\{x\}, \{s\}, \{a\}, t}, \sigma^{\tilde A}_{\{x\}, \{s\}, \{a\}, t})
$$
where
  * $\tilde{A}_{\{x\},\{s\}\{a\}, t} = \sum_{s \in\{s\}} \sum_{a \in\{a\}} \sum_{x \in\{x\}} \sum_{x \sim x', x = x'} N_{x', s, a, t} \cdot \pi_{x', x, s, a, t}$
  * $\sigma_{\{x\},\{s\}\{a\}, t}^{\tilde{A}} = \sqrt{\sum_{s \in\{s\}} \sum_{a \in\{a\}} \sum_{x \in\{x\}} \sum_{x \sim x', x = x'} N_{x', s, a, t} \cdot \pi_{x', x, s, a, t} \cdot \left(1-\pi_{x', x, s, a, t}\right)}$

@@

* Not sure what $R_x$ means. Is it like $R_x: \mathcal{X} \to \mathcal{X}$
* Some confusion on how to offset terms work -- they seem cool though. Might prefer they not be called $\eta$ which is in my head linear predictor
  * $\eta^\lambda_{R_x, s, a, t}$ aren't these $R_x, s, a, t$ specific rather than 
* Aggregation over age 15-49 uses sum from $a = 15$ to $a = 45$? Perhaps this is because $a = 45$ actually corresponds to the age band 45-49. Edit: yes, $a = 45$ corresponds to 45-49
* Sometimes in subscript we have $x, s, a, t$ and sometimes e.g. $x, s, at$ -- why?
* Why $\sigma^\lambda \sim \mathcal{N}^+(0, 1)$ rather than e.g. $\sigma^\lambda \sim \mathcal{N}^+(0, 2.5)$
* Inconsistent use of $T2$ and $T_2$ in the appendix (I prefer the subscript so try to use throughout here)
* In softmax function, confused as to what this equation is saying: shouldn't there be an equals sign in there before the large brackets?
* What's $Y[T2][T1]$ is this a typo and should be $Y[T1]$ -- in "The observed number of HIV positive and already on ART..."
* "In cases where some data inputs, some model..." should be "In cases where some data inputs *are missing*, some model..."
